\Title

### 2020-03-02 manuscript/manuscript.tex
Add gridding differences figures to manuscript

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{multirow}

@@

% Import files with parameter values generated by notebooks
\input{synthetic_model_surveys.tex}
\input{parameters_ground_survey.tex}
\input{parameters_airborne_survey.tex}

@@

The synthetic model is made out of \NPrisms{} prisms distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} between \ModelDepth{} deep and the zero
height plane.
Density contrast of prisms range from \ModelMinDensity{} and
\ModelMaxDensity{}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of
\TargetEastingSize{}$\times$\TargetNorthingSize{} points with a spacing of
\TargetSpacing{} located \TargetHeight{} above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of \TargetEastingSize{}$\times$\TargetNorthingSize{} points
        with a spacing of \TargetSpacing{} located \TargetHeight{} above the
        zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SurveyEasting{}$\times$\SurveyNorthing{}.
The ground survey is composed by \GroundSurveyPoints{} observation points
distributed at heights ranging between \GroundSurveyMinHeight{} and
\GroundSurveyMaxHeight{} (Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has \AirborneSurveyPoints{} points at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SurveyNoise{}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the ground survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

@@

@@

\appendix

\section{Source distributions parameters}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \GroundSourceBellowDataConstantDepthDepth
              & \GroundBlockMedianSourcesConstantDepthDepth
              & \GroundGridSourcesConstantDepthDepth \\
        Spacing & -
                & \GroundBlockMedianSourcesConstantDepthSpacing
                & \GroundGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \GroundGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataRelativeDepthDepth
              & \GroundBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \GroundBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \GroundSourceBellowDataVariableDepthDepth
              & \GroundBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \GroundSourceBellowDataVariableDepthDepthFactor
                     & \GroundBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \GroundSourceBellowDataVariableDepthKNearest
                  & \GroundBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \GroundBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. Depths and spacings are given in km.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth & \AirborneSourceBellowDataConstantDepthDepth
              & \AirborneBlockMedianSourcesConstantDepthDepth
              & \AirborneGridSourcesConstantDepthDepth \\
        Spacing & -
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataRelativeDepthDepth
              & \AirborneBlockMedianSourcesRelativeDepthDepth
              & \\
        Spacing & -
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth & \AirborneSourceBellowDataVariableDepthDepth
              & \AirborneBlockMedianSourcesVariableDepthDepth
              & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing & -
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \\
    \end{tabular}
\end{table*}

>>>>

\documentclass[twocolumn]{article}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\setlength{\columnsep}{2\columnsep}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[round]{natbib}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

@@

The synthetic model is made out of 64 prisms distributed on a region of
\SI{89}{\km}$\times$\SI{88}{\km} between \SI{10}{\km} deep and the zero
height plane.
Density contrast of prisms range from \SI{-900}{\kg\per\cubic\m} and
\SI{500}{\kg\per\cubic\m}.
We created deep big and thin shallow prisms for creating gravity anomalies with
long and short wavelengths, respectively.

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on a regular grid of 56$\times$57 points with a spacing
of \SI{2}{\km} located \SI{2000}{\m} above the zero height plane
(Fig.~\ref{fig:target-grid}).
We will refer to this grid as the \emph{target} grid in the future.

\begin{figure}
    \includegraphics[width=\linewidth]{figs/target-grid.pdf}
    \caption{
        Target grid. Gravitational effect of synthetic model on a regular grid
        composed of 56$\times$57 points with a spacing of \SI{2}{\km} located
        \SI{2000}{\m} above the zero height plane.
    }
    \label{fig:target-grid}
\end{figure}

@@

On both cases we selected only a portion of the survey and rescaled it to span
on an area of \SI{111}{\km}$\times$\SI{111}{\km}.
The ground survey is composed by 963 observation points distributed at heights
ranging between \SI{0}{\m} and \SI{2052}{\m}
(Fig.~\ref{fig:synthetic-ground-survey}(a)).
While the airborne survey has 5673 points at heights between \SI{359}{\m} and
\SI{1255}{\m}.
(Fig.~\ref{fig:synthetic-ground-survey}(a)).

The vertical component of the gravity acceleration generated by the synthetic
model has been computed on both surveys.
Some Gaussian noise (with standard deviation of \SI{1}{\mgal}) has been added
to the effect of the synthetic model to simulate acquisition errors
(Figs.~\ref{fig:synthetic-ground-survey}(b)
and~\ref{fig:synthetic-airborne-survey}(b)).

\begin{figure}
    \includegraphics[width=\linewidth]{figs/ground-survey.pdf}
    \caption{
        Synthetic ground survey.
        (a)~Location of observation points. Altitude given in meters above the
            zero height plane.
        (b)~Vertical component of gravity acceleration generated by the
            synthetic model plus Gaussian noise on the airborne survey
            observation points.
    }
    \label{fig:synthetic-ground-survey}
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/ground_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic ground survey.
    }
    \label{fig:ground-survey-differences}
\end{figure*}

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/airborne_survey_differences.pdf}
    \caption{
        Differences between gravitational effects measured on the target grid
        and the ones produced by the best prediction made by each source
        distribution based on the synthetic airborne survey.
    }
    \label{fig:airborne-survey-differences}
\end{figure*}

@@
